% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US


\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=2099fc]
\definecolor[sectioncolor][h=2099fc]
\definecolor[rulecolor][h=2099fc]
\definecolor[linkcolor][h=205bfc]

% Enable hyperlinks
\setupinteraction[state=start, color=linkcolor]

\setuppapersize [A4][A4]
\setuplayout    
  [
    width=middle, 
    height=middle,
    backspace=20mm,
    cutspace=0mm,
    topspace=10mm,
    bottomspace=20mm,
    header=0mm,
    footer=0mm,
    margin=0pt,
  ]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]
\setupxtable[frame=off,option={stretch,width}]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[title={Dene Farrell},reference={dene-farrell}]

\thinrule

\startblockquote
\useURL[url1][https://github.com/dfarrel1][][github]\from[url1]
\letterbar{}
\useURL[url2][https://www.linkedin.com/in/denefarrell/][][linkedIn]\from[url2]
\letterbar{}
\useURL[url3][https://dfarrel1.github.io/][][resume]\from[url3]
\stopblockquote

\thinrule

\startblockquote
Enabling data driven decision making through well-architected cloud
solutions.
\stopblockquote

\thinrule

\subsection[title={Experience},reference={experience}]

{\bf \useURL[url4][https://www.dds.mil/][][Defense Digital
Service]\from[url4], Rogue Squadron} - Data Architect\crlf
Washington DC, November 2020 - Present

\startitemize
\item
  Designed, developed and deployed a real-time streaming analytics
  platform for ingestion of and machine learning on IoT data.
\item
  Established a cloud-based data brokering service allowing for
  integration of external data producers and data consumers across the
  DoD.
\stopitemize

{\bf \useURL[url5][https://www.latch.com/][][Latch]\from[url5]} - Senior
Manager, Data Engineering\crlf
New York, Sept 2019 -- Nov 2020

\startitemize
\item
  Managed a team of five including three data engineers, a data
  scientist, and a business analyst
\item
  Delivered several cross-company services: Data Centralization and
  Governance, Data Ecosystem Management with Automated Analytics,
  Company Operational Notifications, CRM to ERP Integration, PII
  Anonymization, ML Pipeline Development and Deployment Framework.
\item
  Coordinated central data platform initiatives with diverse
  stakeholders while constantly adapting to meet the day-to-day data
  needs at Latch.
\stopitemize

{\bf \useURL[url6][https://www.capitalone.com/tech/][][Capital
One]\from[url6]} - Principal Data Engineer\crlf
New York, May 2017 -- Sept 2019

\startitemize
\item
  Lead Card-on-file Detections: Successfully deployed a classification
  pipeline that identifies for all credit card holders which merchants
  have stored their credentials on file.
\item
  Developed a general purpose data visualization tool for handling
  highly inter-related categorical variables at high volumes, high state
  variability, low documentation and low stability. Leveraged Spark and
  D3. Implemented on credit card transaction data.
\item
  Re-architected a monolith ML application to microservices using AWS
  serverless services.
\item
  Implemented a comprehensive customer profile feature engineering
  pipeline to service a multi-armed bandit call schedule recommendation
  service with Python, Snowflake, and Kubernetes.
\stopitemize

{\bf \useURL[url7][https://insightfellows.com/][][Insight Fellows
Program]\from[url7]} - Data Engineering Fellow\crlf
New York, Jan.~2017 -- Mar.~2017

\startitemize
\item
  Deployed Fleetingly, a taxi fleet analysis application for scalable
  sensing of geospatial patterns
\item
  Implemented fleet performance analysis with live streaming and
  historical pattern visualizations.
\item
  Tech stack: Kafka, Spark Streaming, ElasticSearch, Kibana. {[}Python +
  Scala{]}
\stopitemize

{\bf \useURL[url8][https://www.mskcc.org/research/ski/labs/jennifer-zallen][][Sloan
Kettering Institute]\from[url8]} - Software Engineer\crlf
New York, Dec.~2008 -- Jan.~2017

\startitemize
\item
  Built image processing applications for understanding early Drosophila
  embryo development.
\item
  Made advanced computational tools accessible to non-technical users
  with intuitive interfaces.
\item
  Enhanced image processing capabilities in order to analyze previously
  unobtainable 4D data.
\item
  Co-authored several publication in premiere journals such as Nature.
\item
  Built applications with Matlab, Python, and Java
\stopitemize

\subsection[title={Education},reference={education}]

\startdescription{2008}
  {\bf M.S., Systems Science}; State University of New York, Binghamton
\stopdescription

\startdescription{2006}
  {\bf B.S., Bioengineering}; State University of New York, Binghamton
\stopdescription

\subsection[title={Side Projects},reference={side-projects}]

{\bf Gifthorse Inc} - Founder and Developer\crlf
New York, June 2018 -- Present

\startitemize
\item
  Developed a fun and easy to use gift recommender service
\item
  Django Web Backend, React Frontend, Scala Data Engineering and ML
  Backend
\item
  Services implemented: product parsing and updating, basic frontend
  functionality, basic recommendation functionalities, authentication,
  CICD Deployments
\stopitemize

\subsection[title={Skills},reference={skills}]

\startdescription{Programming Languages}
  {\bf Python:} 8 Years experience.

  {\bf Scala:} 3 years experience developing in Scala. Completed Courses
  from EPFL in Functional Programming and Software Development with
  Scala.

  {\bf JavaScript, Typescript, React:} 2 years experience. I use
  JavaScript and React in my side project, Gifthorse and leveraged
  typescript most recently at DDS to contribute to web app products.

  {\bf SQL:} I have built several products that leverage RDS (Postgres),
  Snowflake, Spark SQL and Teradata. Additionally I have build and
  integrate with NOSQL systems such as MongoDB, Elasticsearch, and
  DynamoDB.

  {\bf Shell (Bash):} e.g.
  \useURL[url9][https://github.com/dfarrel1/dots][][dots]\from[url9]

  Basic knowledge:\crlf
  {\bf C++}, {\bf Java}, {\bf D3}, {\bf Mathematica}, {\bf Matlab},
  {\bf Perl}
\stopdescription

\startdescription{Data Engineering}
  AWS, Sagemaker, Kafka, Spark, EMR, DynamoDB, AWS Lambda, Flask,
  Django, ElasticSearch, Airflow, Luigi, Ansible, Jenkins, CircleCI,
  Snowflake, Docker, Kubernetes, System Architecture and System Design,
  Looker
\stopdescription

\startdescription{Machine Learning}
  Classification, Regression, Data Wrangling, Feature Engineering,
  Entity Resolution, Artificial Neural Networks, Unsupervised Learning
  Algorithms, K-Means Clustering, PCA, Data Visualization
\stopdescription

\startdescription{Team Management}
  Roadmap Planning, Jira, Agile, Scrum, Kanban, Stakeholder
  Communication, Software Team Productivity Enhancements, Architecture
  Decision Records, Software and Data System Documentation Strategies
\stopdescription

\thinrule

\startblockquote
\useURL[url10][mailto:dene.farrell@gmail.com][][dene.farrell@gmail.com]\from[url10]
• 914.602.3847 • New York
\stopblockquote

\thinrule

\startblockquote
\useURL[url11][https://dfarrel1.github.io/index.pdf][][pdf]\from[url11]
•
\useURL[url12][https://dfarrel1.github.io/index.txt][][txt]\from[url12]
•
\useURL[url13][https://dfarrel1.github.io/index.docx][][doc]\from[url13]
• \useURL[url14][https://dfarrel1.github.io/][][web]\from[url14] •
\useURL[url15][https://github.com/dfarrel1/dfarrel1.github.io/][][generator]\from[url15]
•
\useURL[url16][https://dfarrel1.github.io/one-page/Dene-Farrell-resume-2021-June-onepage.pdf][][one-page]\from[url16]
•
\useURL[url17][https://dfarrel1.github.io/one-page/Dene-Farrell-CV-2021-June.pdf][][cv+publications]\from[url17]
\stopblockquote

\stoptext
